---
title: "How Great Am I?"
output:
  html_document:
    df_print: paged
---

## Introduction
Let's investigate Google Scholar's data on the impact of my (meager) 
research publications!

```{r, results='hide', message=FALSE}
include <- function(library_name){
  if( !(library_name %in% installed.packages()) )
    install.packages(library_name) 
  library(library_name, character.only=TRUE)
}
include("rvest")
include("tidyr")
```

First, let's load the html from my Scholar page:
```{r}
my_url <- "https://scholar.google.com/citations?user=KmIt5HIAAAAJ&hl=en"
scholar_html <- read_html(my_url)
```
We should note that this page only (initially) loads the top 20 articles, sorted by most citations.
However, that is a good enough starting place. From this page, let's "scrape" the data that matters:
*article title*, *citations*, *year*

```{r}
publications <- scholar_html %>% html_nodes(".gsc_a_tr")

article_titles <- publications %>% 
                    html_nodes("td.gsc_a_t > a") %>% 
                    html_text()
citations <- publications %>% 
              html_nodes("td.gsc_a_c > a") %>% 
              html_text() %>% 
              as.integer()
years <- publications %>% 
          html_nodes("td.gsc_a_y > span") %>% 
          html_text() %>% 
          as.integer()

research <- tibble(year= years, title= article_titles, citations= citations)
```

## Analysis
```{r}
print(research)
```
How many citations are there per paper?
```{r}
mean(research$citations)
```

## Conclusion

How great am I? *The Data says*... **meh.**